{ \fontfamily{ptm}\selectfont First Order Nonsmooth Optimization: Algorithm Design, Variational analysis, and Applications }

### 2024-12-29 Notebook LaTEX/Proposal/main.tex
>w<, changes

\section{Introduction}
    Let $\RR^n$ be the ambient space. We consider 
    \begin{align}
        \min_{x \in \RR^n} \left\lbrace
            F(x): f(x) + g(x)
        \right\rbrace.
    \end{align}\label{eqn:additive-comp-obj}
    Unless specified, assume $f:\RR^n \rightarrow \RR$ is $L$-Lipscthiz smooth $\mu \ge 0$ strongly convex and $g:Q \rightarrow \overline \RR$ is convex. 
    This type of problem is referred to as additive composite problems in the literature. 
    \par
    Our ongoing research concerns accelerated proximal gradient type method for solving (\ref{eqn:additive-comp-obj}). 
    In the expository writing by Walkington \cite{noel_nesterovs_nodate}, a variant for of accelerated gradient method for strongly convex function $f$ is discussed. 
    We had two lingering questions after reading it. 
    \begin{enumerate}
        \item Do there exist a unified description for the convergence for both variants of the algorithms?
        \item Is it possible to attain faster convergence rate without knowledge about the strong convexity of function $f$?
        \item Is it possible to describe the convergence of function value for momentum sequences that are much weaker than the Nesterov's rule? 
    \end{enumerate}
    The good news is we have definitive answers for all questions by our own efforts of research. 
    Section \ref{sec:unify-nes-acceleration}, \ref{sec:spectral-momentum} are our ongoing research which present the answers to the questions. 
    \par
    In Section \ref{sec:unify-nes-acceleration}, we proposed the method of ``Relaxed Weak Accelerated Proximal Gradient (R-WAPG)'' as the foundation to describe several variants of Accelerated proximal gradient method in the literatures. 
    The convergence theories of R-WAPG allows us to model convergence of accelerated proximal gradient method where the momentum sequence doesn't strictly follow the conditions presented in the literatures. 
    The descriptive power of R-WAPG allows convergence analysis for all the variants using one single theorem. 
    \par
    In Section \ref{sec:spectral-momentum} we propose a practical algorithm that exploits a specific term in the proof of R-WAPG to achieve faster convergence for solving (\ref{eqn:additive-comp-obj}) without knowing parameter $L, \mu$ in prior. 
    Results of numerical experiments are presented. 
    \par
    Section \ref{sec:catalyst} are results of literatures review in MATH 590. 
    \todo{Add citations here. }{\hl{It's based on a series of papers}} in the topic of Catalyst Meta Acceleration method for First Order Variance Reduced Methods. 
    We will point out potential future direction of research of Catalyst acceleration. 
    \par
    Section \ref{sec:pep}, \ref{sec:inexact-prox}, \ref{sec:nes-acc-ncnvx} preview literatures in  nonsmooth optimization frontier research where progress and impacts can be made.  
    \subsection{Theme of the research}
        This section specifies a theme of the research in this proposal. 
        Out first objective is to explore the Goldilocks zones between these topics: theories of variational analysis, design of continuous optimization algorithm and applications in sciences, engineering, and statistics.  
        Our second objective is to identify the ``chemistry" occurring between properties of functions and the designs of continuous optimizations algorithm and how it impacts the convergence and behaviors of the algorithms.

\section{Preliminaries}
    \todoinline{
        Clarify: Notations,
        Organizations. 
    }
    This section contains the basics of contents from convex optimization, and variational analysis. 
    \begin{enumerate}
        \item $\overline \RR := \RR \cup \{\infty, -\infty\}$
    \end{enumerate}
    \subsection{Fundamentals in non-convex analysis}
        \todoinline{\noindent
            We are in $\RR^n$, and the weakest assumption we are making for the objective function is Local Lipschitz continuity. 
            Definitions: 
            \begin{enumerate}
                \item[$\blacksquare$] Local Lipschitz continuity. 
                \item[$\square$]Regular subgradient. Remember to cite. 
                \item[$\square$] Limiting subgradient. Remember to cite. 
                \item[$\blacksquare$] Weakly convex function. 
                \item[$\blacksquare$]The Bregman Divergence of function. 
            \end{enumerate}
            Take Limiting, Regular subgradient definitions from Cui, Pong's book, Definition 4.3.1. 
        }
        Let the ambient space be $\RR^n$ equipped with inner product and 2-norm. 
        Let $O$ be an open subset of $\RR^n$, the weakest assumption we are making for the objective function $F: O \subseteq \RR^n \rightarrow \RR$ for optimization problem is Local Lipschitz Continuity. 
        The assumption of local Lipschitz continuity is weak enough to describe most problems in applications, and strong enough to avoid most pathologies in analysis.

@@

                    v \in \RR^n \left| 

@@

            \begin{lemma}[Proximal gradient model function]\;\\
                Take $\widetilde{\mathcal M}^{L^{-1}}, \mathcal M^{L^{-1}}$ as defined in this section, we will have for all $x \in \RR^n$ that: 
                \begin{align*}
                    \widetilde{\mathcal M}^{L^{-1}}(x; y)
                    &= 
                    \mathcal M^{L^{-1}}(x; y)- D_f(x, y).
                \end{align*}
            \end{lemma}
            \begin{lemma}[A favorable property of gradient mapping]
                Take $F:= f + g$ as defined in this section. 
                Fix any $x \in \RR^n$. 
                Then there exists $v \in \partial g(T_L x)$ such that $\mathcal G_L (x) = v + \nabla f(x)$. 
            \end{lemma}
            \begin{remark}
                This lemma still holds for non-convex $f$ under prox-boundness and weak convexity and differentiability of $f$. 
            \end{remark}
            \begin{lemma}[The proximal gradient inequality]\label{thm:prox-grad-ineq}
                Take $F:= f + g$ as defined in this section. 
                Fix any $y \in \RR^n$, then for all $x$, the proximal gradient inequality is true: 
                \begin{align*}
                    (\forall x \in \RR^n)\quad 
                    h(x)  - h(Ty) - \langle L(y - Ty), x - y\rangle
                    - \frac{\mu}{2}\Vert x - y\Vert^2 - \frac{L}{2}\Vert y - Ty\Vert^2 
                    &\ge 0. 
                \end{align*}
            \end{lemma}
            \begin{remark}
                This lemma is proved in our draft paper. 
            \end{remark}

    \subsection{Nesterov's Estimating sequence technique}
        \todoinline{\noindent
            Do the following: 
            \begin{enumerate}
                \item What is Nesterov's estimating sequence. 
                \item How is it used to derive the algorithm and convergence rate of algorithm. 
                \item Where is it used and why is it important here. 
            \end{enumerate}
        }
        \todoinline{
            Examples
            \begin{enumerate}
                \item Example estimating sequence. 
            \end{enumerate}
        }

@@

    The proofs haven't been carefully verified by people other than the author yet. 

@@

    \todo{Cite Nesterov's original paper on this. }{\hl{Proposed back in 1983 the original Nesterov's acceleration method}} which uses the previous iterates to extrapolate the next iterate to evaluate the gradient. 
    It's well known that, if minimizer $x^*$ exists for $F$, the method achieves a $\mathcal O(1/k^2)$ convergence rate on the objective value $F(x_k)$. 
    \todo{Cite Chapter 2 of Nesterov's new book. }{\hl{This convergence rate is considered optimal for all class of $L$ Lipschitz smooth convex function}}. 

@@

    \todo{Cite Beck 2009 FISTA. }{\hl{Beck and Toubelle}} mitigate the issue by restarting and showed that it still has a $\mathcal O(1/k^2)$ convergence rate, and it performs better empirically. 
    \todo{Cite Necoara linear convergence, and Aujol 2024 Parameter free FISTA restart. }{\hl{See}} and references within for recent advancements in restarting accelerated proximal gradient algorithm.

@@

    As introduced previously, in \todo{Cite Walkington's education stuff here. }{\hl{Walkington's writing}}, he showed that there exists a variant of the Nesterov's accelerated gradient method that achieved a linear convergence rate of $\mathcal O((1 - \sqrt{\kappa})^k)$ where $\kappa = \mu/L$. 

@@

    \todo{Cite them.}{\hl{The same variant also appears in Beck's book as V-FISTA, and Nesterov's book as (2.2.22).}} 

@@

    \todo{Cite them. }{\hl{Chambolle, Dossal}} showed that by choosing sequence $(t_k)_{k \ge 1}$ to be $t_k = (n + a - 1)/a$ where $a > 2$ instead would give $(x_k)_{k \ge 0}$ weak convergence in Hilbert space. 

@@

        Our second main result shows that there exists $\rho_k > 1$ such that our R-WAPG reduces to a variant of FISTA proposed in \todo{Fix citation here.}{\hl{Chambolle, Dossal}} \cite{chambolle_convergence_2015}, and we are able to show the same convergence rate in Theorem \ref{thm:r-wapg-on-cham-doss}. 
        When $\rho_k = 1, \mu = 0$, R-WAPG reduces perfectly to FISTA by Beck \cite{beck_first-order_2017}, if $\mu > 0, \rho_k = 1$, it reduces to the V-FISTA by Beck \cite{beck_first-order_2017}. 

@@

        Organization now follows. 
        \todoinline{Finish the organizations here after this section is finished. }
    \subsection{Building Blocks of R-WAPG}
                \item[$\blacksquare$] R-WAPG stepwise definition.
                \item[$\blacksquare$] R-WAPG stepwise convergence claim.
            Todo: 
                \item Explain what is what. 
        \begin{definition}[Stepwise weak accelerated proximal gradient]\label{def:stepwise-wapg}\;\\
            Assume $0 \le \mu < L$.
            Fix any $k \in \mathbb Z$. 
            For any $(v_k, x_k), \alpha_k \in (0, 1), \gamma_k > 0$, let $\hat \gamma_{k + 1}$, and vectors $y_k, v_{k + 1}, x_{k + 1}$ be given by: 
                \hat \gamma_{k + 1} &= (1 - \alpha_k)\gamma_k + \mu \alpha_k, 
                y_k &= 
                (\gamma_k + \alpha_k \mu)^{-1}(\alpha_k \gamma_k v_k + \hat\gamma_{k + 1} x_k), 
                g_k &= \mathcal G_L y_k, 
                v_{k + 1} &= \hat\gamma^{-1}_{k + 1}
                (\gamma_k(1 - \alpha_k) v_k - \alpha_k g_k + \mu \alpha_k y_k), 
                x_{k + 1} &= T_L y_k. 

@@

    \subsection{R-WAPG Sequence and R-WAPG algorithm}
            The R-WAPG Algorithm and convergence claim. 
                \item[$\blacksquare$] R-WAPG Sequence.
                \item[$\blacksquare$] R-WAPG algorithm
                \item[$\blacksquare$] Convergence of the R-WAPG algorithm.
            Todo: 
                \item Explain what is what. 
        \begin{definition}[R-WAPG sequences]\label{def:rwapg-seq}\;\\
            Assume $0 \le \mu < L$. 
            The sequences $(\alpha_k)_{k \ge 0}, (\rho_k)_{k \ge1}$ are sequences parameterized by $\mu, L$. 
            They are valid for R-WAPG if all the following holds: 
            We call $(\alpha_k)_{k \ge 0}, (\rho_k)_{k \ge 0}$ the \textbf{R-WAPG Sequences}. 
        \begin{definition}[Relaxed weak accelerated proximal gradient (R-WAPG)]\label{def:wapg}\;\\
            Choose any $x_1 \in \RR^n, v_1 \in \RR^n$. 
            Let $(\alpha_k)_{k \ge0}, (\rho_k)_{k \ge 0}$ be given by Definition \ref{def:rwapg-seq}. 
            The algorithm generates a sequence of vector $(y_k, x_{k + 1}, v_{k + 1})_{k \ge 1}$ for $k\ge 1$ by the procedures:  
                For $k=1, 2, 3, \cdots$
                    \gamma_k &:= \rho_{k -1}L\alpha_{k - 1}^2, 
                    \hat \gamma_{k + 1} & := (1 - \alpha_k)\gamma_k + \mu \alpha_k = L\alpha_k^2, 
                    y_k &= 
                    (\gamma_k + \alpha_k \mu)^{-1}(\alpha_k \gamma_k v_k + \hat\gamma_{k + 1} x_k), 
                    g_k &= \mathcal G_L y_k, 
                    v_{k + 1} &= 
                    \hat\gamma^{-1}_{k + 1}
                    (\gamma_k(1 - \alpha_k) v_k - \alpha_k g_k + \mu \alpha_k y_k), 
                    x_{k + 1} &= T_L y_k. 
        \begin{proposition}[R-WAPG convergence claim]\label{prop:wagp-convergence}\; \\
            Fix any arbitrary $x^* \in \RR^n, N \in \mathbb N$. 
            Let vector sequence $(y_k, v_{k}, x_{k})_{k \ge 1}$ and R-WAPG sequences $\alpha_k, \rho_k$ be given by Definition \ref{def:wapg}. 
            Define $R_1 = 0$ and suppose that for $k = 1, 2, \cdots, N$, we have $R_k$ recursively given by: 
                R_{k + 1}
                := 
                \frac{1}{2}\left(
                    L^{-1} - \frac{\alpha_k^2}{\hat \gamma_{k + 1}}
                \right)\Vert g_k\Vert^2
                + 
                (1 - \alpha_k)
                    \epsilon_k + R_k + 
                    \frac{\mu\alpha_k\gamma_k}{2\hat \gamma_{k + 1}}
                    \Vert v_k - y_k\Vert^2
            Then for all $k = 1, 2, \cdots, N$: 
                & F(x_{k + 1}) - F(x^*) + \frac{L \alpha_k^2}{2}\Vert v_{k + 1} - x^*\Vert^2
                    F(x_1) - F(x^*) + \frac{L\alpha_0^2}{2}\Vert v_1 - x^*\Vert^2

    \subsection{Equivalent forms of R-WAPG algorithm}
                \item[$\blacksquare$] R-WAPG Intermediate form.
                \item[$\blacksquare$] R-WAPG Similar triangle form. 
                \item[$\blacksquare$] R-WAPG Momentum form. 
            Theorems: 
                \item[$\blacksquare$] R-WAPG First equivalent form. 
                \item[$\blacksquare$] R-WAPG Second equivalent form.
                \item[$\blacksquare$] R-WAPG Third equivalent form.
            Lemmas
            Todo: 
                \item Explain what is what. 

>>>>

\section{Introduction}
    Let $\RR^n$ be the ambient space. We consider 
    \begin{align}
        \min_{x \in \RR^n} \left\lbrace
            F(x): f(x) + g(x)
        \right\rbrace.
    \end{align}\label{eqn:additive-comp-obj}
    Unless specified, assume $f:\RR^n \rightarrow \RR$ is $L$-Lipscthiz smooth $\mu \ge 0$ strongly convex and $g:Q \rightarrow \overline \RR$ is convex. 
    This type of problem is referred to as additive composite problems in the literature. 
    \par
    Our ongoing research concerns accelerated proximal gradient type method for solving (\ref{eqn:additive-comp-obj}). 
    In the expository writing by Walkington \cite{noel_nesterovs_nodate}, a variant for of accelerated gradient method for strongly convex function $f$ is discussed. 
    We had two lingering questions after reading it. 
    \begin{enumerate}
        \item Do there exist a unified description for the convergence for both variants of the algorithms?
        \item Is it possible to attain faster convergence rate without knowledge about the strong convexity of function $f$?
        \item Is it possible to describe the convergence of function value for momentum sequences that are much weaker than the Nesterov's rule? 
    \end{enumerate}
    The good news is we have definitive answers for all questions by our own efforts of research. 
    Section \ref{sec:unify-nes-acceleration}, \ref{sec:spectral-momentum} are our ongoing research which present the answers to the questions. 
    \par
    In Section \ref{sec:unify-nes-acceleration}, we proposed the method of ``Relaxed Weak Accelerated Proximal Gradient (R-WAPG)'' as the foundation to describe several variants of Accelerated proximal gradient method in the literatures. 
    The convergence theories of R-WAPG allows us to model convergence of accelerated proximal gradient method where the momentum sequence doesn't strictly follow the conditions presented in the literatures. 
    The descriptive power of R-WAPG allows convergence analysis for all the variants using one single theorem. 
    \par
    In Section \ref{sec:spectral-momentum} we propose a practical algorithm that exploits a specific term in the proof of R-WAPG to achieve faster convergence for solving (\ref{eqn:additive-comp-obj}) without knowing parameter $L, \mu$ in prior. 
    Results of numerical experiments are presented. 
    \par
    Section \ref{sec:catalyst} are results of literatures review in MATH 590. 
    \todo{$\square$ Add Lin's papers and Paquette's papers.  }{\hl{It's based on a series of papers}} in the topic of Catalyst Meta Acceleration method for First Order Variance Reduced Methods. 
    We will point out potential future direction of research of Catalyst acceleration. 
    \par
    Section \ref{sec:pep}, \ref{sec:inexact-prox}, \ref{sec:nes-acc-ncnvx} preview literatures in  nonsmooth optimization frontier research where progress and impacts can be made.  
    \subsection{Theme of the research}
        This section specifies a theme of the research in this proposal. 
        Out first objective is to explore the Goldilocks zones between these topics: theories of variational analysis, design of continuous optimization algorithm and applications in sciences, engineering, and statistics.  
        Our second objective is to identify the ``chemistry'' occurring between properties of functions and the designs of continuous optimizations algorithm and how it impacts the convergence and behaviors of the algorithms.

\section{Preliminaries}
    \todoinline{
        Clarify: Notations,
        Organizations. 
    }
    This section contains the basics of contents from convex optimization, and variational analysis. 
    \par
    Notations. 
    \begin{enumerate}
        \item $\overline \RR := \RR \cup \{\infty, -\infty\}$
    \end{enumerate}
    \subsection{Fundamentals in non-convex analysis}
        \todoinline{\noindent
            We are in $\RR^n$, and the weakest assumption we are making for the objective function is Local Lipschitz continuity. 
            Definitions: 
            \begin{enumerate}
                \item[$\blacksquare$] Local Lipschitz continuity. 
                \item[$\square$]Regular subgradient. Remember to cite. 
                \item[$\square$] Limiting subgradient. Remember to cite. 
                \item[$\blacksquare$] Weakly convex function. 
                \item[$\blacksquare$]The Bregman Divergence of function. 
            \end{enumerate}
            Take Limiting, Regular subgradient definitions from Cui, Pong's book, Definition 4.3.1. 
        }
        Let the ambient space be $\RR^n$ equipped with inner product and 2-norm. 
        Let $O$ be an open subset of $\RR^n$, the weakest assumption we are making for the objective function $F: O \subseteq \RR^n \rightarrow \RR$ for optimization problem is Local Lipschitz Continuity. 
        The assumption of local Lipschitz continuity is weak enough to describe most problems in applications, and strong enough to avoid most pathologies in analysis.

@@

                    v \in \RR^n \left| \; 

@@

            \begin{lemma}[Proximal gradient model function]\;\\
                Take $\widetilde{\mathcal M}^{L^{-1}}, \mathcal M^{L^{-1}}$ as defined in this section, we will have for all $x \in \RR^n$ that: 
                \begin{align*}
                    \widetilde{\mathcal M}^{L^{-1}}(x; y)
                    &= 
                    \mathcal M^{L^{-1}}(x; y)- D_f(x, y).
                \end{align*}
            \end{lemma}
            \begin{lemma}[A favorable property of gradient mapping]
                Take $F:= f + g$ as defined in this section. 
                Fix any $x \in \RR^n$. 
                Then there exists $v \in \partial g(T_L x)$ such that $\mathcal G_L (x) = v + \nabla f(x)$. 
            \end{lemma}
            \begin{remark}
                This lemma still holds for non-convex $f$ under prox-boundedness and weak convexity and differentiability of $f$. 
            \end{remark}
            \begin{lemma}[The proximal gradient inequality]\label{thm:prox-grad-ineq}
                Take $F:= f + g$ as defined in this section. 
                Fix any $y \in \RR^n$, then for all $x$, the proximal gradient inequality is true: 
                \begin{align*}
                    (\forall x \in \RR^n)\quad 
                    h(x)  - h(Ty) - \langle L(y - Ty), x - y\rangle
                    - \frac{\mu}{2}\Vert x - y\Vert^2 - \frac{L}{2}\Vert y - Ty\Vert^2 
                    &\ge 0. 
                \end{align*}
            \end{lemma}
            \begin{remark}
                This lemma is proved in our draft paper. 
            \end{remark}

    \subsection{Nesterov's estimating sequence technique}
            Do the following: 
                \item What is Nesterov's estimating sequence. 
                \item How is it used to derive the algorithm and convergence rate of algorithm. 
                \item Where is it used and why is it important here. 
            Examples
                \item Example estimating sequence. 
        The method of Nesterov's estimating sequence for accelerated gradient method, and their nonsmooth counterparts assumes a convex function $F: \RR^n \rightarrow \overline{\RR}$. 
        The estimating sequence is a technique searching for candidate algorithm with extrapolated momentum, and proving their convergence rate if possible. 
        The method is widespread in the literatures, and the ideas behind it are tremendously useful. 
        \todo{$\square$ Add Guler's 1992 new proximal point paper. \\ $\square$ Cite it. }{\hl{Güler}} 
        used the method to design an accelerated proximal point method, which inspired and served as the foundation of Catalyst Acceleration for variance reduced method in machine learning. 
        \todo{$\square$ Add the paper: ``Accelerating the cubic regularization of Newton’s method on convex
        problems''\\ $\square$ Cite it.}{\hl{Nesterov}}
        also used the techinique to design an accelerated cubic regularized Newton's method. 
        In 
        \todo{$\square$ Cite it. }\hl{Chapter 6 of Nesterov's book}, it's also used to derive a method of accelerated mirror descent. 
        And finally, 
        \todo{$\square$ Add paper: ``Accelerated regularized newton methods for
        minimizing composite convex functions'' \\ $\square$ Cite it. }{\hl{Geovani N. et al}}
        used the technique to derive a accelerated Newton's method for convex composite objective function. 
        The definition of the estimating sequence that follows is based on our own understanding of the estimating sequence. 
        \begin{definition}[Nesterov's estimating sequence]\label{def:nes-est-seq}
            Let $\phi_k : \RR^n \rightarrow\RR$ for all $k \ge 0$ be a sequence of functions. 
            We call this sequence of function a Nesterov's estimating sequence when it satisfies the conditions: 
                \item There exists another sequence $(x_k)_{k \ge 0}$ such that for all $k \ge 0$ it has $F(x_k) \le \phi_k^*: =\min_{x}\phi_k(x)$. 
                \item There exists a sequence of $(\alpha_k)_{k \ge 0}$ where $\alpha_k \in (0, 1)\; \forall k \ge0 $ such that for all $x \in \RR^n$ it has $\phi_{k + 1}(x) - \phi_k(x) \le - \alpha_k(\phi_k(x) - F(x))$. 
        \begin{observation}
            In general, identifying the sequence $(x_k)_{k \ge 0}$ is non-trivial. 
            But in case it can be found, the method of estimating sequence gives us the convergence rate described by the sequence $(\alpha_k)_{k \ge 0}$, and a candidate algorithm that generates the sequence $(x_k)_{k \ge 0}$. 
            It's two birds with one stone. 
            If we define $\phi_k$, $\Delta_k(x) := \phi_k (x) - F(x)$ for all $x \in \RR^n$ and assume that $F$ has minimizer $x^*$. 
            Then observe that $\forall k \ge 0$:  
                \Delta_k(x) 
                &= \phi_k(x) - F(x) \ge \phi_k^* - F(x)
                x = x_k\implies 
                \Delta_k(x_k) 
                &\ge 
                \phi_k^* - F(x_k) \ge 0;
                x = x_* \implies 
                \Delta_k(x_*)
                &\ge \phi_k^* - F_* \ge F(x_k) - F_* \ge 0. 
            The function $\Delta_k(x)$ is non-negative at points: $x_*, x_k$.
            We can derive the convergence rate of $\Delta_k(x^*)$ because $\forall x \in \RR^n$: 
                \phi_{k + 1}(x) - \phi_k(x) 
                &\le - \alpha_k (\phi_k(x) - F(x))
                \phi_{k + 1}(x) - F(x) - (\phi_k(x) - F(x))
                -\alpha_k(\phi_k(x) - F(x))
                \Delta_{k + 1}(x) - \Delta_k(x) &\le
                - \alpha_k\Delta_k(x)
                \Delta_{k + 1}(x) 
                (1 - \alpha_k)\Delta_k(x). 
            Unrolling the above recursion it yields: 
                \Delta_{k + 1}(x) &\le 
                (1 - \alpha_k)\Delta_k(x) \le \cdots \le 
                    \prod_{i = 0}^k(1 - \alpha_i)
                \right)\Delta_0(x). 
            Finally, by setting $x = x^*$, $\Delta_k(x^*)$ is non-negative and using the property of Nesterov's estimating sequence it gives: 
                F(x_k) - F(x^*) \le \phi_k^* - F(x^*) \le \Delta_k(x^*) = \phi_k(x^*) - F(x^*) \le \left(\prod_{i = 0}^k(1 - \alpha_i)\right)\Delta_0(x^*).

        \end{observation}

@@

    The proofs haven't been carefully verified by authoratative people other than the author yet. 

@@

    \todo{$\square$ Add Nesterov's original paper. \\ $\square$ Cite it.  }{\hl{Proposed back in 1983 the original Nesterov's acceleration method}} 
    which uses the previous iterates to extrapolate the next iterate to evaluate the gradient. 
    It's well known that if minimizer $x^*$ exists for $F$, the method achieves a $\mathcal O(1/k^2)$ convergence rate on the objective value $F(x_k)$. 
    \todo{$\square$ Add Nesterov's new book. \\ $\square$ Cite it.}{\hl{This convergence rate is considered optimal for all class of $L$ Lipschitz smooth convex function}}. 

@@

    \todo{$\square$ Add Beck 2009 FISTA original paper. $\square$ Cite it.}{\hl{Beck and Toubelle}} 
    mitigated the issue by restarting and showed that it still has a $\mathcal O(1/k^2)$ convergence rate, and it performs better empirically. 
    \todo{$\square$ Add Necoara linear convergence \\ $\square$ Add Aujol 2024 Parameter free FISTA restart. \\ $\square$ Cite Section 5.2.2 for the former, cite the entirety for the later. }{\hl{See}} 
    and references within for recent advancements in restarting accelerated proximal gradient algorithm.

@@

    As introduced previously, in 
    \todo{$\square$ Add Neol J. Walkington's ``Nesterov’s Method for Convex  Optimization''. \\ $\square$ Cite it. }{\hl{Walkington's writing}}, 
    he showed that there exists a variant of the Nesterov's accelerated gradient method that achieved a linear convergence rate of $\mathcal O((1 - \sqrt{\kappa})^k)$ where $\kappa = \mu/L$. 

@@

    \todo{$\square$ Add Beck's first order textbook\\ $\square$ Cite 10.7.7. \\ $\square$ Add Nesterov's textbook. \\ $\square$ Cite it. }{\hl{The same variant also appears in Beck's book as V-FISTA, and Nesterov's book as (2.2.22).}} 

@@

    \todo{$\square$ Add paper: ``On the convergence of the iterates of the...''\\ $\square$ Cite them. }{\hl{Chambolle, Dossal}} 
    showed that by choosing sequence $(t_k)_{k \ge 1}$ to be $t_k = (n + a - 1)/a$ where $a > 2$ instead would give $(x_k)_{k \ge 0}$ weak convergence in Hilbert space. 

@@

        Our second main result shows that there exists $\rho_k > 1$ such that our R-WAPG reduces to a variant of FISTA proposed in 
        \todo{$\square$ Add ``On the convergence of the iterates of...'' \\ $\square$ Cite them. }{\hl{Chambolle, Dossal}}, 
        and we are able to show the same convergence rate in Theorem \ref{thm:r-wapg-on-cham-doss}. 
        When $\rho_k = 1, \mu = 0$, R-WAPG reduces perfectly to FISTA by in 
        \todo{$\square$ Add beck's original FISTA Paper. \\$\square$ Cite it. }
        {\hl{Beck}}. 
        If $\mu > 0, \rho_k = 1$, it reduces to the V-FISTA by Beck \cite{beck_first-order_2017}. 

@@

        \todoinline{$\blacksquare$ Finish the organizations here after this section is finished. }

        Organization now follows. 
        Section \ref{ssec:building-block-rwapg} provides a stepwise description of the R-WAPG iterative algorithm along with an inequality crucial to proving the convergence rate later. 
        Section \ref{ssec:rwpag-seq-and-alg} introduce the definition of an R-WAPG sequence, which constraints all possible parameters used permitted by the algorithm.
        The section also states the full R-WAPG algorithm and an upper bound on $F(x_k) - F(x^*)$. 
        Here, $x_k$ is generated by the R-WAPG algorithm and $x^*$ is the minimizer. 
        Section \ref{ssec:quiv-repr-rwapg} bring forward three equivalent forms of the R-WAPG algorithm making it more comparable with other Acceerated Proximal Gradient method appeared in the literatures. 
        Section \ref{ssec:describe-variants-with-rwapg} gives characterizations of specific R-WAPG sequence that leads to convergence of the R-WAPG algorithm in terms of the optimality gap. 
        The section also identifies specific instance of permissible R-WAPG sequences where it fits with the FISTA, V-FISTA, and the algorithm proposed by 
        \todo{$\square$ Cite the Chambolle, Dossal 2015 paper here again. }{\hl{Chambolle Dossal}}.

    \subsection{Building Blocks of R-WAPG}\label{ssec:building-block-rwapg}
        \todoinline{\noindent
            Definitions: 
            \begin{enumerate}
                \item[$\blacksquare$] R-WAPG stepwise definition.
                \item[$\blacksquare$] R-WAPG stepwise convergence claim.
            \end{enumerate}
            To do: 
            \begin{enumerate}
                \item[$\blacksquare$] Explain what is what. 
            \end{enumerate}
        }
        Definition\ref{def:stepwise-wapg} describes the procedures of generating the iterates $(v_{k + 1}, x_{k + 1})$ given any $(v_k, x_k)$ and parameter $\alpha_k \in (0, 1), \gamma_k > 0$. 
        Proposition \ref{prop:stepwise-lyapunov} gives an inequality instrumental to the convergence rate analysis, with the same assumption as the definition.

        \begin{definition}[Stepwise weak accelerated proximal gradient]\label{def:stepwise-wapg}\;\\
            Assume $0 \le \mu < L$.
            Fix any $k \in \mathbb Z$. 
            For any $(v_k, x_k), \alpha_k \in (0, 1), \gamma_k > 0$, let $\hat \gamma_{k + 1}$, and vectors $y_k, v_{k + 1}, x_{k + 1}$ be given by: 
            \begin{align*}
                \hat \gamma_{k + 1} &= (1 - \alpha_k)\gamma_k + \mu \alpha_k, 
                \\
                y_k &= 
                (\gamma_k + \alpha_k \mu)^{-1}(\alpha_k \gamma_k v_k + \hat\gamma_{k + 1} x_k), 
                \\
                g_k &= \mathcal G_L y_k, 
                \\
                v_{k + 1} &= \hat\gamma^{-1}_{k + 1}
                (\gamma_k(1 - \alpha_k) v_k - \alpha_k g_k + \mu \alpha_k y_k), 
                \\
                x_{k + 1} &= T_L y_k. 
            \end{align*}
        \end{definition}

@@

    \subsection{R-WAPG Sequence and R-WAPG algorithm}\label{ssec:rwpag-seq-and-alg}
        \todoinline{\noindent
            The R-WAPG Algorithm and convergence claim. 
            Definitions: 
            \begin{enumerate}
                \item[$\blacksquare$] R-WAPG Sequence.
                \item[$\blacksquare$] R-WAPG algorithm
                \item[$\blacksquare$] Convergence of the R-WAPG algorithm.
            \end{enumerate}
            Todo: 
            \begin{enumerate}
                \item[$\blacksquare$] Explain what is what. 
            \end{enumerate}
        }
        The Definition \ref{def:wapg} gives the definition of an iterative algorithm we called: Relaxed Weak Accelerated Proximal Gradient (R-WAPG) algorithm which generates sequence $(x_k, v_k)_{k \ge 1}$ using the R-WAPG sequences $(\alpha_k)_{k \ge 0}, (\rho_k)_{k \ge 0}$ given in Defintion \ref{def:rwapg-seq}. 
        Proposition \ref{prop:wagp-convergence} shows the upper bound of the optimality gap $F(x_k) - F(x^*)$ with $(x_k)$ generated by the R-WAPG algorithm.

        \begin{definition}[R-WAPG sequences]\label{def:rwapg-seq}\;\\
            Assume $0 \le \mu < L$. 
            The sequences $(\alpha_k)_{k \ge 0}, (\rho_k)_{k \ge1}$ are sequences parameterized by $\mu, L$. 
            They are valid for R-WAPG if all the following holds: 
            \begin{align*}
                \alpha_0 &\in (0, 1], 
                \\
                \alpha_k &\in (\mu/L, 1) \quad (\forall k \ge 1), 
                \\
                \rho_k &:= \frac{\alpha_{k + 1}^2 - (\mu/L)\alpha_{k + 1}}{(1 - \alpha_{k + 1})\alpha_k^2} \quad \forall (k \ge 0). 
            \end{align*}
            We call $(\alpha_k)_{k \ge 0}, (\rho_k)_{k \ge 0}$ the \textbf{R-WAPG Sequences}. 
        \end{definition}
        \begin{definition}[Relaxed weak accelerated proximal gradient (R-WAPG)]\label{def:wapg}\;\\
            Choose any $x_1 \in \RR^n, v_1 \in \RR^n$. 
            Let $(\alpha_k)_{k \ge0}, (\rho_k)_{k \ge 0}$ be given by Definition \ref{def:rwapg-seq}. 
            The algorithm generates a sequence of vector $(y_k, x_{k + 1}, v_{k + 1})_{k \ge 1}$ for $k\ge 1$ by the procedures:  
            \begin{tcolorbox}
                For $k=1, 2, 3, \cdots$
                \begin{align*}
                    \gamma_k &:= \rho_{k -1}L\alpha_{k - 1}^2, 
                    \\
                    \hat \gamma_{k + 1} & := (1 - \alpha_k)\gamma_k + \mu \alpha_k = L\alpha_k^2, 
                    \\
                    y_k &= 
                    (\gamma_k + \alpha_k \mu)^{-1}(\alpha_k \gamma_k v_k + \hat\gamma_{k + 1} x_k), 
                    \\
                    g_k &= \mathcal G_L y_k, 
                    \\
                    v_{k + 1} &= 
                    \hat\gamma^{-1}_{k + 1}
                    (\gamma_k(1 - \alpha_k) v_k - \alpha_k g_k + \mu \alpha_k y_k), 
                    \\
                    x_{k + 1} &= T_L y_k. 
                \end{align*}    
            \end{tcolorbox}
        \end{definition}
        \begin{proposition}[R-WAPG convergence claim]\label{prop:wagp-convergence}\; \\
            Fix any arbitrary $x^* \in \RR^n, N \in \mathbb N$. 
            Let vector sequence $(y_k, v_{k}, x_{k})_{k \ge 1}$ and R-WAPG sequences $\alpha_k, \rho_k$ be given by Definition \ref{def:wapg}. 
            Define $R_1 = 0$ and suppose that for $k = 1, 2, \cdots, N$, we have $R_k$ recursively given by: 
            \begin{align*}
                R_{k + 1}
                := 
                \frac{1}{2}\left(
                    L^{-1} - \frac{\alpha_k^2}{\hat \gamma_{k + 1}}
                \right)\Vert g_k\Vert^2
                + 
                (1 - \alpha_k)
                \left(
                    \epsilon_k + R_k + 
                    \frac{\mu\alpha_k\gamma_k}{2\hat \gamma_{k + 1}}
                    \Vert v_k - y_k\Vert^2
                \right). 
            \end{align*} 
            Then for all $k = 1, 2, \cdots, N$: 
            \begin{align*}
                & F(x_{k + 1}) - F(x^*) + \frac{L \alpha_k^2}{2}\Vert v_{k + 1} - x^*\Vert^2
                \\
                &\le 
                \left(
                    \prod_{i = 0}^{k - 1} \max(1, \rho_{k})
                \right)
                \left(
                    \prod_{i = 1}^{k} \left(1  - \alpha_i\right)
                \right)
                \left(
                    F(x_1) - F(x^*) + \frac{L\alpha_0^2}{2}\Vert v_1 - x^*\Vert^2
                \right). 
            \end{align*}
        \end{proposition}
